Standalone Tactics using OpenTheory

### 2012-02-13 paper.tex
clarify last sentence of conclusion
some space-saving tweaks
(Mike's suggestions)

As an example, suppose the user of an interactive theorem prover is faced with the goal
\[
\forall n.\ 8\le n\Rightarrow\exists s,t.\ n = 3s + 5t
\]
decides to pass it off to a standalone tactic for linear arithmetic.\footnote{This is a representation of the problem asking for a proof that \pounds 3 and \pounds 5 coins can be used to make \pounds $n$ for any natural number $n$ that is at least 8.}

@@

The main advantage to using \OpenTheory for communication is that it provides a standard, independent framework for fixing the meanings of constants between different systems.
For example, the numerals $3$, $5$ and $8$ in the example goal term can be encoded in binary using the standard constants \texttt{Number.Natural.bit0} and \texttt{Number.Natural.bit1}.
The full names and properties of these constants are indicated in the \OpenTheory standard library, and interactive theorem provers can maintain translations to and from their local names and theorems.
A system using a different encoding for numbers (say unary, with \texttt{Number.Natural.suc} and \texttt{Number.Natural.zero}) could use additional standalone tactics to translate between encodings.

@@

There are two approaches to obtaining a standalone tactic: either write one directly; or extract an existing tactic from an interactive theorem prover.
We have experimented with the second approach, extracting tactics from HOL4 and from HOL Light.
The procedure is reasonably lightweight, but less flexible than writing a standalone tactic directly.
For tactic extraction to succeed, the key requirements of the interactive theorem prover are:
\begin{enumerate}
\item\label{req:io} An \OpenTheory article file reader and writer.

\item\label{req:log} A facility for recording proofs and converting them to the \OpenTheory logical kernel.

\item\label{req:ckpt} A facility for making a standalone executable encompassing the tactic functionality without the usual interface to the interactive theorem prover.
\end{enumerate}

@@

We have shown how, using \OpenTheory for communication, we can write tools for higher order logic reasoning tasks as standalone tactics, making them available to multiple interactive theorem provers and independently maintainable.
Existing proof tools can be extracted from their home systems for reuse.
There is a substantial but hopefully tolerable overhead of communicating goals and proofs over the web.

>>>>

As an example, suppose the user of an interactive theorem prover is faced with the goal
\[
\forall n.\ 8\le n\Rightarrow\exists s,t.\ n = 3s + 5t
\]
decides to pass it off to a standalone tactic for linear arithmetic.

@@

The main benefit of using \OpenTheory for communication is that it provides a standard, independent framework for fixing the meanings of constants between different systems.
For example, the numerals $3$, $5$ and $8$ in the example goal term can be encoded in binary using the standard constants \texttt{Number.Natural.bit0} and \texttt{Number.Natural.bit1}.
The full names and properties of these constants are indicated in the \OpenTheory standard library, and interactive theorem provers can maintain translations to and from their local names and theorems.
A system using a different encoding for numbers (say unary, with \texttt{Number.Natural.suc} and \texttt{Number.Natural.zero}) could use additional standalone tactics to translate between encodings.

@@

There are two approaches to obtaining a standalone tactic: either write one directly; or extract an existing tactic from an interactive theorem prover.
We have experimented with the second approach, extracting tactics from HOL4 and from HOL Light.
The procedure is reasonably lightweight, but less flexible than writing a standalone tactic directly.
For tactic extraction to succeed, the key requirements of the interactive theorem prover are:
\begin{enumerate}
\item\label{req:io} Ability to read and write \OpenTheory article files.

\item\label{req:log} Ability to record proofs and present them over the \OpenTheory kernel.

\item\label{req:ckpt} Ability to make a standalone executable encompassing the tactic functionality without the usual interface to the interactive theorem prover.
\end{enumerate}

@@

We have shown how, using \OpenTheory for communication, we can write tools for higher order logic reasoning tasks as standalone tactics, making them available to multiple interactive theorem provers and independently maintainable.
Existing proof tools can be extracted from their home systems for reuse.
There is a substantial but hopefully tolerable overhead of communicating goals and proofs in article files over the web.
